Conjure: Summoning Proxies from Unused Address Space

### 2019-09-26 paper/paper.tex
add cite, typo

We implemented a mask site mimicking proxy, that pretends to be a mask site
when actively probed by the censor. Once the station accepts accepts a connection 
for a registered flow, it initially acts as a transparent
proxy to a mask site specified by the client during registration. The
application parses the handshake, forwarding packets back and forth between
client and mask site without modification, extracting the server and client
randoms. The application attempts to decrypt the first application data record
from the client using a key derived from the secret seed, client, and server
randoms. We use the uTLS library~\cite{utls} on both the application and client
to allow us to change the TLS secrets being used after the handshake.

@@

We evaluated the performance of a client from an India-based VPS,
Figures~\ref{fig:upload} and~\ref{fig:download} show the upload and download as
measured by iperf for TapDance, our \scheme implementation (using the mask site application),
and a direct connection to our iperf server in the ISP's network.

>>>>

We implemented a mask site mimicking proxy, that pretends to be a mask site
when actively probed by the censor. Once the station accepts accepts a connection 
for a registered flow, it initially acts as a transparent
proxy to a mask site specified by the client during registration. The
application parses the handshake, forwarding packets back and forth between
client and mask site without modification, extracting the server and client
randoms. The application attempts to decrypt the first application data record
from the client using a key derived from the secret seed, client, and server
randoms. We use the uTLS library~\cite{utls,tls-fingerprint} on both the application and client
to allow us to change the TLS secrets being used after the handshake.

@@

We evaluated the performance of a client from an India-based VPS.
Figures~\ref{fig:upload} and~\ref{fig:download} show the upload and download bandwidth as
measured by iperf for TapDance, our \scheme implementation (using the mask site application),
and a direct connection to our iperf server in the ISP's network.
